AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-09 publications/iaai21/dora_outlier_detection_iaai.tex
add negative sampling reference #42

   When working with science datasets, OOD detection can be used for 
   cleaning datasets, e.g., flagging ground-truth labels with GPS or human
    entry error or identifying wrongly categorized objects in a catalog. 
    It could also be used for discovery, e.g., to flag novel samples in order 
    to guide instrument acquisition or scientific analysis. Another application
   is the detection of rare objects that are known to exist but the known
   examples are too few to create a large enough labeled dataset for 
   supervised classification algorithms. 
  Despite wide differences in applications, data types, and dimensionality,
 the same underlying machine learning algorithms can be employed across 
 all of these domains. A challenge for applying them however is that domain
 scientists do not always have the programming or machine learning background
 to apply the algorithms themselves using existing tools. Given the widespread 
 applicability and transferability of OOD methods, the scientific community 
 would benefit from a tool that made it easy for them to apply popular outlier
 detection algorithms to their science datasets. We created DORA (Domain-
 agnostic Outlier Ranking Algorithms) to provide a tool for applying outlier 
 detection algorithms to a variety of scientific data sets with minimal coding
 required. Users need only to specify details for their data/application 
 including the data type, location, and algorithms to run in an experiment
 configuration file. DORA supports image, raster, time series, 
or feature vector input data types and outlier detection methods that include
 Isolation Forest, Discovery via Eigenbasis Modeling of Uninteresting Data 
 (DEMUD)~\citep{wagstaff:demud13}, principal component analysis (PCA),
   Reed-Xiaoli (RX) detector,  
 Local RX, negative sampling, and probabilistic autoencoder. Given a set of
  data samples, each algorithm assigns an outlier score to each sample. DORA
   provides results organization and visualization modules to help users 
   process the results, including sorting samples by outlier score, evaluating 
   outlier recall for a set of known/labeled outliers, clustering groups of 
   similar outliers together, and causal graphs. To demonstrate the 
   cross-domain applicability of DORA, we conducted outlier detection
    experiments for three real-world use cases: 1) cleaning noisy ground-truth 
    datasets (Earth Science), 
     2) flagging non-astrophysical objects in the Dark Energy Survey 
     (astrophysics), and 3) novelty-guided onboard targeting of instruments
      for Mars rovers (planetary science). [We showed that ...]

>>>>

   When working with science datasets, OOD detection can be used for 
   cleaning datasets, e.g., flagging ground-truth labels with GPS or human
    entry error or identifying wrongly categorized objects in a catalog. 
    It could also be used for discovery, e.g., to flag novel samples in order 
    to guide instrument acquisition or scientific analysis. Another application
   is the detection of rare objects that are known to exist but the known
   examples are too few to create a large enough labeled dataset for 
   supervised classification algorithms. 
  Despite wide differences in applications, data types, and dimensionality,
 the same underlying machine learning algorithms can be employed across 
 all of these domains. A challenge for applying them however is that domain
 scientists do not always have the programming or machine learning background
 to apply the algorithms themselves using existing tools. Given the widespread 
 applicability and transferability of OOD methods, the scientific community 
 would benefit from a tool that made it easy for them to apply popular outlier
 detection algorithms to their science datasets. We created DORA (Domain-
 agnostic Outlier Ranking Algorithms) to provide a tool for applying outlier 
 detection algorithms to a variety of scientific data sets with minimal coding
 required. Users need only to specify details for their data/application 
 including the data type, location, and algorithms to run in an experiment
 configuration file. DORA supports image, raster, time series, 
or feature vector input data types and outlier detection methods that include
 Isolation Forest, Discovery via Eigenbasis Modeling of Uninteresting Data 
 (DEMUD)~\citep{wagstaff:demud13}, principal component analysis (PCA),
   Reed-Xiaoli (RX) detector,  
 Local RX, negative sampling~\cite{sipple:neg-sampling20}, and probabilistic 
 autoencoder. Given a set of data samples, each algorithm assigns an outlier 
 score to each sample. DORA provides results organization and visualization 
 modules to help users process the results, including sorting samples by outlier 
 score, evaluating outlier recall for a set of known/labeled outliers, clustering 
 groups of similar outliers together, and causal graphs. To demonstrate the 
 cross-domain applicability of DORA, we conducted outlier detection experiments 
 for three real-world use cases: 1) cleaning noisy ground-truth datasets (Earth 
 Science), 2) flagging non-astrophysical objects in the Dark Energy Survey 
 (astrophysics), and 3) novelty-guided onboard targeting of instruments for Mars 
 rovers (planetary science). [We showed that ...]
